---
title: "linear model from Web"
author: "April Galvan"
date: "Fall 2021"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

The scatterplot looks as if the points are going uphill to the right. My suspicion is that this plot is a positive correlation due to the fact that the scatterplot is going uphill to the right.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation we have found is 0.69, which is a positive correlation.

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equation of a line is y=mx+b.
The fit equation is SIMS=0.054563*ARM - 4.095160

#### Predict at target point

SIMS=0.054563*88 - 4.095160

```{r}
0.054563*88 - 4.095160
```

When we plugged in 88 for arm in our best fit equation, we got 0.706, and that will be our prediction.

```{r}
new <- data.frame(ARM = 88,GRIP = 94)
```

```{r}
predict(model.1,new)
```

Using the predict function, it also gives us the same result, 0.706384.

#### scatterplot with model fit

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point() + geom_smooth(method=lm)
```

Here is the best fit line for our data, and we can see that if we look for an x-value of 88 for ARM, the y-value is about 0.7 as predicted.


## Model 2 SIM~GRIP

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

This scatterplot also shows that the points go uphill to the right. My prediction is that this is a positive correlation.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

GRIP has a smaller correlation with SIMS at 0.64, compared to SIMS with ARM, which is 0.69.

### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  

If we look at the Adjusted R-squared value of this GRIP data, it is smaller than the ARM data's Adjusted R-squared. In addition, the residual standard error is larger for this GRIP data than the ARM data. In conclusion based off these values, Model 1 is doing a better job at explaining our prediction and it's the better model. 

#### predict model.2 at target point

```{r}
predict(model.2,new)
```

SIMS=0.045463*94-4.809675

```{r}
0.045463*94 - 4.809675
```

Our prediction value is -0.5361543.

#### now add the model fit to our plot for model.2

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
basicNN + geom_point() + geom_smooth(method=lm)
```

Here is the result of the scatterplot and our best fit line for our GRIP and SIMS data. If we use our prediction value, it matches x-value = 0.94 for GRIP.

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

We have a positive correlation between using both ARM and GRIP data. The correlation we got using both ARM and GRIP at the same time is higher than using either ARM or GRIP by themselves.

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```  

Fit equation is SIMS=-5.43 + GRIP * 0.02 + ARM * 0.04

#### predict model.3 at target point

Our residual standard error is 1.144 which is smaller than our other models. Also our multiple R-squared is bigger, which makes this a better fit model.

```{r}
predict(model.3,new, interval = "prediction")
```

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

